\bf An Examination of Sport Climbing Competition Format and Scoring System

### 2021-09-07 manuscript/Rmd/draft.tex
Restructure manuscript

\hypertarget{rank-correlation}{%
\subsection{Rank Correlation}\label{rank-correlation}}

@@

\hypertarget{leave-one-climber-out-analysis}{%
\subsection{Leave-one-climber-out
Analysis}\label{leave-one-climber-out-analysis}}

\caption{This figure illustrates the changes to the final rankings of the 2018 Youth Olympics Men's and Women's Finals when we leave out one climber. For each gender competition, each panel represents the rank of the drop-out athlete, with 0 being the original final results. Each case with a change in rank orderings is highlighted by a black panel border, and any player with a rank change is represented by a red-filled bar}\label{fig:unnamed-chunk-20}
\end{figure}

\hypertarget{rank-swapping-analysis}{%
\subsection{Rank Swapping Analysis}\label{rank-swapping-analysis}}

\hypertarget{principal-component-analysis}{%
\subsection{Principal Component
Analysis}\label{principal-component-analysis}}

@@

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-23-1}

@@

\caption{Women's Qualification PCA}\label{fig:unnamed-chunk-23}
\end{figure}

@@

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-24-1} \end{center}

@@

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-25-1}

@@

\caption{Men's Qualification PCA}\label{fig:unnamed-chunk-25}
\end{figure}

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-26-1} \end{center}

>>>>

\hypertarget{correlation-analysis}{%
\subsection{Correlation Analysis}\label{correlation-analysis}}

\hypertarget{rank-correlation}{%
\subsubsection{Rank Correlation}\label{rank-correlation}}

@@

\hypertarget{principal-component-analysis}{%
\subsubsection{Principal Component
Analysis}\label{principal-component-analysis}}

@@

@@

\caption{Women's Qualification PCA}\label{fig:unnamed-chunk-20}
\end{figure}

@@

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-21-1} \end{center}

@@

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-22-1}

@@

\caption{Men's Qualification PCA}\label{fig:unnamed-chunk-22}
\end{figure}

\begin{center}\includegraphics{draft_files/figure-latex/unnamed-chunk-23-1} \end{center}

\hypertarget{sensitivity-analysis}{%
\subsection{Sensitivity Analysis}\label{sensitivity-analysis}}

\hypertarget{leave-one-climber-out-analysis}{%
\subsubsection{Leave-one-climber-out
Analysis}\label{leave-one-climber-out-analysis}}

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-26-1}

\caption{This figure illustrates the changes to the final rankings of the 2018 Youth Olympics Men's and Women's Finals when we leave out one climber. For each gender competition, each panel represents the rank of the drop-out athlete, with 0 being the original final results. Each case with a change in rank orderings is highlighted by a black panel border, and any player with a rank change is represented by a red-filled bar}\label{fig:unnamed-chunk-26}
\end{figure}

\hypertarget{rank-swapping-analysis}{%
\subsubsection{Rank Swapping Analysis}\label{rank-swapping-analysis}}
